Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-21 awipev-CO2.Rmd
- rename ph_s_sf_temp_mix to ph_s_sf_temp_insi - now use pressure_insitu_ctd rather than 11 m to calculate ph_s_sf_temp_insi

```{r read and prepare discrete data, echo=FALSE, warning=FALSE, message=FALSE}
d <- read.table(paste0(path, "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv"), header = T, dec = ".", as.is = T, sep = ";", fill = TRUE)
#d$datetime <- as.POSIXct(d$sampling_date, format="%d/%m/%Y %H:%M", tz="UTC")
d$datetime <- dmy_hm(d$sampling_date, tz="UTC")
d$measure_date <- dmy(d$measure_date, tz="UTC")
d$date <- as.Date(d$datetime)

@@

# Fill "at/ct" to all line with same day.
at_ct_mean <- d %>% 
  group_by(datetime)%>%
  dplyr::summarize(at_mean = mean(at, na.rm = T),
                   ct_mean = mean(ct, na.rm = T),
                   at_sd = sd(at, na.rm = T), 
                   ct_sd = sd(ct, na.rm = T)
                   )
d <- left_join(d, at_ct_mean, by='datetime')
# Fill the gaps in at_mean with interpolation
TAinterp <-approx(d$datetime, d$at_mean, xout=d$datetime, method="linear", rule=2)
names(TAinterp) <- c("datetime", "at_mean_interp")
TAinterp <- as.data.frame(TAinterp)
d$at_mean_interp <- TAinterp$at_mean_interp

@@

# add sal_fb + sal_insitu_ctd + temp_fb + temp_insitu_ctd from d_all into d, to use pHinsi
# use the closest time to add them
closest <- which.closest(d$datetime, d_all$datetime) # closest date and time
d$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
d$closest_datetime[abs(d$datetime - d_all$datetime[closest]) > 30*60] <- NA
# create closest_datetime in d_all (copy of datetime)
d_all$closest_datetime <- d_all$datetime
d <- left_join(d, d_all%>%dplyr::select(c(closest_datetime, sal_fb, temp_fb, temp_mix, sal_mix, temp_insitu_ctd)), by="closest_datetime")

# Conversion of spectro pH to insitu mix T°
pH_seafet <- d %>%
  dplyr::filter(!is.na(pH_s_seafet) & !is.na(temp_insitu_ctd) )
pH_seafet <- pH_seafet %>%
  dplyr::mutate(ph_s_sf_temp_mix = pHinsi(pH = pH_seafet$pH_s_seafet, ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = pH_seafet$temp_insitu_ctd, Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$depth/10, S = pH_seafet$sal_mix, Pt = 0, Sit = 0))

@@

# Make mean for replicates. create separate seafet/durafet df to join to initial "d" df
pH_seafet_mean <- pH_seafet%>%
  dplyr::select(datetime, ph_s_sf_temp_mix)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(ph_s_sf_temp_mix = mean(ph_s_sf_temp_mix, na.rm = T))
pH_durafet_mean <- pH_durafet%>%
  dplyr::select(datetime, ph_s_dur_temp_fb)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(ph_s_dur_temp_fb = mean(ph_s_dur_temp_fb, na.rm = T))

@@

# seaFET pH 
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, ph_s_sf_temp_mix) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")
d_all <- d_all %>% 
  dplyr::mutate(ph_s_sf_temp_mix = ifelse(n_depth_ctd == 4, ph_s_sf_temp_mix, NA)) %>% # eliminate ph spectro data when the profiler was at several depth during the same hour
  dplyr::mutate(ph_s_sf_temp_mix = ifelse(!is.na(temp_insitu_ctd_7m) | !is.na(temp_insitu_ctd_9m), 
                                          ph_s_sf_temp_mix, NA)) # only use ph spectro data when profiler was below 6 m

@@

# # We decided to calibrate pH data within each pH spectro measurement.
# # Thus, each pH spectro is taken as one calibration periode. 
# # We calculate here the day between 2 pH spectro in order to have the start/end of one deployment period.
# sfPeriod <- d_all%>%
#   dplyr::select(datetime, ph_s_sf_temp_mix)%>%
#   dplyr::filter(!is.na(ph_s_sf_temp_mix))
# # Remove pH spectro that not allow a calibration because of missing calibration value (voltINT, Sal or Temp insi)
# sfPeriod <- sfPeriod%>%
# dplyr::filter(datetime != "2018-04-16 07:00:00" & datetime != "2018-12-14 09:00:00" & datetime != "2019-01-18 09:00:00")
# 
# sfPeriod <-  sfPeriod %>%
#   dplyr::arrange(datetime) %>%
#   dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(sfPeriod)])/2* 3600)))%>%
#   dplyr::mutate(sf_interval = datetime + middle[2:nrow(sfPeriod)])
# 
# #put interval in a list with the start date of seaFET measurements
# sfinterv <- c( as_datetime("2017-08-24 13:00:00"), sfPeriod[,4])
# #Change period sfinterv[5]. make the end of this period longer until 2018-03-21 23:59:00 
# # This is needed in order to take in consideration pH from March 2018 with a calibration E0 lower (-1.4) than the next period (-0.38).
# sfinterv[5] <- ymd_hms("2018-03-22 23:59:59")
# #  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
# # sfinterv[6] <- ymd_hms("2018-04-24 18:00:00")
# #  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
# # sfinterv[14] <- ymd_hms("2019-01-29 16:00:00")
# 
# #sfinterv <-sort(unlist(sfinterv, use.names=FALSE))
# # set deployment period between 2 spectro measurements.

@@

# pco2_contros_xts <-
#   dplyr::select(d_all, datetime, voltINT, voltEXT, sal_fb, temp_insitu_ctd, ph_s_sf_temp_mix)
# pco2_contros_xts <-
#   as.xts(pco2_contros_xts, order.by = d_all$datetime)
# dygraph(pco2_contros_xts,
#         group = "awipev",
#         main = "<i>p</i>CO<sub>2</sub>",
#         ylab = "<i>p</i>CO<sub>2</sub>") %>%
#   dySeries(
#     axis = "y2",
#     "voltINT",
#     label = "voltINT",
#     color =  RColorBrewer::brewer.pal(5, "Dark2")[1],
#     strokeWidth = 0,
#     pointSize = 2
#   ) %>%
#   dySeries(axis="y2",
#     "voltEXT",
#     label = "voltEXT",
#     color =  RColorBrewer::brewer.pal(5, "Dark2")[2],
#     strokeWidth = 0,
#     pointSize = 2
#   ) %>%
#    dySeries(
#     "temp_insitu_ctd",
#     label = "temp_insitu_ctd",
#     color =  RColorBrewer::brewer.pal(5, "Dark2")[3],
#     strokeWidth = 0,
#     pointSize = 2
#   ) %>%
#    dySeries(
#     "sal_fb",
#     label = "sal_fb",
#     color =  RColorBrewer::brewer.pal(5, "Dark2")[4],
#     strokeWidth = 0,
#     pointSize = 2
#   ) %>%
#    dySeries(
#     "ph_s_sf_temp_mix",
#     label = "ph_s_sf_temp_mix",
#     color =  RColorBrewer::brewer.pal(5, "Dark2")[5],
#     strokeWidth = 0,
#     pointSize = 4
#   ) %>%
#   dyHighlight(
#     highlightCircleSize = 8,
#     highlightSeriesBackgroundAlpha = 0.5,
#     hideOnMouseOut = TRUE
#   ) %>%
#   dyLegend(show = "follow")   %>%
#   dyAxis("y2",valueRange = c(-2,2))%>%
#   dyOptions(
#     drawGrid = TRUE,
#     drawPoints = TRUE,
#     pointSize = c(1, 8, 1),
#     useDataTimezone = TRUE
#   ) %>%
#   dyRangeSelector(height = 30, dateWindow = NULL)

@@

####
## calculation of E0INT25/E0EXT25 ##
##     new sf_calib function      ##
####
calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_mix, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
# put number of deployment 
calib_spectro$deployment_sf <- d_all$deployment_sf

@@

# add spectro points that cannot be taken into consideration (some ancillary data T and/or S not available)
# shown as white triangles on the plot
d_all <- d_all %>%
  dplyr::mutate(
    pH_s_sf_no_calb = ifelse(
      datetime == as.POSIXct("2018-04-16 07:00:00") |
        datetime == as.POSIXct("2018-12-14 10:00:00") |
        datetime == as.POSIXct("2019-01-18 11:00:00"),
      ph_s_sf_temp_mix,
      NA
    )
  )

@@

seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_mix, pHint_tot_sf, pH_s_sf_no_calb)
seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
dygraph(seafet_depth_xts, group = "depth", main="pH seaFET (ref + corrected + raw)", ylab="pHT") %>%
dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 3) %>%
dySeries("ph_s_sf_temp_mix", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
dySeries("pH_s_sf_no_calb", label = "pH spectro no calibration", color =  "black", pointShape = "triangle", strokeWidth = 0, pointSize = 6 ) %>%
dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="UTC"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="UTC"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="UTC"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="UTC"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= Sys.Date(), color = "#E0E0E0") %>%
  dyLegend(show = "auto")   %>%
  dyAxis("y2",valueRange = c(-2, 2)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)

@@

```{r pHs comparaison sf spectro, echo=FALSE, message= FALSE, warning=FALSE}
# Spectro / seafet
# fit <- lmodel2(data = d_all,  ph_s_sf_temp_mix ~ pHint_tot_sf , nperm = 99)
#
# p_sf_spectro <-  ggplot(d_all,aes(x=pHint_tot_sf, y= ph_s_sf_temp_mix, label = month))+
#   geom_text( aes(color=factor(month))) +
#   scale_color_discrete(guide = "none")+
#  geom_abline(slope=1, intercept =0, linetype = "dashed") +
#   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
#   labs(title = paste("pH spectro vs pH seaFET","\n Adj R2 = ", signif(fit$rsquare, 3),
#                      "; Intercept =", signif(fit$regression.results[2,2], 3),
#                      "; Slope =", signif( fit$regression.results[2,3], 3),
#                      "; P =", signif(fit$P.param, 3))) +
#   theme(aspect.ratio=1,plot.title = element_text(size=7)) +
#     coord_fixed(ratio = 1 , xlim=c(8,8.2), ylim=c(8,8.2))+
#   labs(x="pH seaFET", y="pH spectro, 4°C ", color = "Months") + theme_bw()
# p_sf_spectro
```

@@

#### Script awipev-co2.Rmd which runs locally
* reads locally fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds
* sal_mix: when ferrybox data (sal_fb) are missing, they are replaced by data from the profiling ctd for depths > 8 m (sal_insitu_ctd_9m)
* temp_mix: when data of in situ temperature at 11 m (temp_insitu_11m) are missing, they are replaced by data from the profiling ctd for depths > 8 m
* pco2_calc: pco2 calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
* calibrate seafet pH
    - ph_s_sf_temp_mix: pH spectro seaFET pH insi calculé avec AT interpolée + temp_mix +sal_mix
    - E0int25_sf: calculé à partir du voltage interne + ph_s_sf_temp_mix (temp 11m + temp_insitu_ctd_9m si trous) + temp CTD 9m + sal CTD 9m (calib seaFET fonction 1)
    - phint_tot_sf: calculé à partir du voltage interne + E0 + temp CTD + sal CTD (calib seaFET fonction 2)
* ph_calc: pH calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
* despike pH seaFET
* calibrate durafet pH
    - ph_s_dur_temp_fb: pH spectro durafet pH insi calculé avec AT interpolée + temp_fb +sal_fb
* Relation at / sal_mix 
* at_calc: calculé from sal_mix
* saves locally d_all.rds which comprises all variables plus those generated in the script

>>>>

```{r read and prepare discrete data, echo=FALSE, warning=FALSE, message=FALSE}
d <- tibble(
  read.table(paste0(path, "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv"), header = T, dec = ".", as.is = T, sep = ";", fill = TRUE)
)
#d$datetime <- as.POSIXct(d$sampling_date, format="%d/%m/%Y %H:%M", tz="UTC")
d$datetime <- dmy_hm(d$sampling_date, tz="UTC")
d$measure_date <- dmy(d$measure_date, tz="UTC")
d$date <- as.Date(d$datetime)

@@

# mean at and ct
at_ct_mean <- d %>% 
#  group_by(datetime)%>%
  group_by(date) %>%
  dplyr::summarize(at_mean = mean(at, na.rm = T),
                   ct_mean = mean(ct, na.rm = T),
                   at_sd = sd(at, na.rm = T), 
                   ct_sd = sd(ct, na.rm = T)
                   )
d <- left_join(d, at_ct_mean, by='date') %>% 
  dplyr::select(datetime, date, temp_s_lab, pH_s_seafet, pH_s_durafet, location_flag, at_mean, ct_mean) %>% # removed useless variables and also to do unique next
  dplyr::distinct()

# Fill the gaps in at_mean with interpolation
TAinterp <-approx(d$datetime, d$at_mean, xout=d$datetime, method="linear", rule=2)
names(TAinterp) <- c("datetime", "at_mean_interp")
TAinterp <- as.data.frame(TAinterp)
d$at_mean_interp <- TAinterp$at_mean_interp

@@

# add sal_fb + sal_insitu_ctd + temp_fb + temp_insitu_ctd from d_all into d, to use pHinsi
# use the closest time to add them
closest <- which.closest(d$datetime, d_all$datetime) # closest date and time
d$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
d$closest_datetime[abs(d$datetime - d_all$datetime[closest]) > 30*60] <- NA
# create closest_datetime in d_all (copy of datetime)
d_all$closest_datetime <- d_all$datetime
d <- left_join(d, d_all %>% dplyr::select(c(closest_datetime, sal_fb, temp_fb, temp_mix, sal_mix, temp_insitu_ctd, pressure_insitu_ctd)), by="closest_datetime")

# Conversion of spectro pH to insitu mix T°
pH_seafet <- d %>%
  dplyr::filter(!is.na(pH_s_seafet) & !is.na(temp_insitu_ctd))
pH_seafet <- pH_seafet %>%
  dplyr::mutate(ph_s_sf_temp_insi = pHinsi(pH = pH_seafet$pH_s_seafet, ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = pH_seafet$temp_insitu_ctd, Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd, S = pH_seafet$sal_mix, Pt = 0, Sit = 0))

@@

# Make mean for replicates. create separate seafet/durafet df to join to initial "d" df
pH_seafet_mean <- pH_seafet%>%
  dplyr::select(datetime, ph_s_sf_temp_insi)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(ph_s_sf_temp_insi = mean(ph_s_sf_temp_insi, na.rm = T))
pH_durafet_mean <- pH_durafet%>%
  dplyr::select(datetime, ph_s_dur_temp_fb)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(ph_s_dur_temp_fb = mean(ph_s_dur_temp_fb, na.rm = T))

@@

# seaFET pH 
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, ph_s_sf_temp_insi) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")
d_all <- d_all %>% 
  dplyr::mutate(ph_s_sf_temp_insi = ifelse(n_depth_ctd == 4, ph_s_sf_temp_insi, NA)) %>% # eliminate ph spectro data when the profiler was at several depth during the same hour
  dplyr::mutate(ph_s_sf_temp_insi = ifelse(!is.na(temp_insitu_ctd_7m) | !is.na(temp_insitu_ctd_9m), 
                                          ph_s_sf_temp_insi, NA)) # only use ph spectro data when profiler was below 6 m

@@

# # We decided to calibrate pH data within each pH spectro measurement.
# # Thus, each pH spectro is taken as one calibration periode. 
# # We calculate here the day between 2 pH spectro in order to have the start/end of one deployment period.
# sfPeriod <- d_all%>%
#   dplyr::select(datetime, ph_s_sf_temp_insi)%>%
#   dplyr::filter(!is.na(ph_s_sf_temp_insi))
# # Remove pH spectro that not allow a calibration because of missing calibration value (voltINT, Sal or Temp insi)
# sfPeriod <- sfPeriod%>%
# dplyr::filter(datetime != "2018-04-16 07:00:00" & datetime != "2018-12-14 09:00:00" & datetime != "2019-01-18 09:00:00")
# 
# sfPeriod <-  sfPeriod %>%
#   dplyr::arrange(datetime) %>%
#   dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(sfPeriod)])/2* 3600)))%>%
#   dplyr::mutate(sf_interval = datetime + middle[2:nrow(sfPeriod)])
# 
# #put interval in a list with the start date of seaFET measurements
# sfinterv <- c( as_datetime("2017-08-24 13:00:00"), sfPeriod[,4])
# #Change period sfinterv[5]. make the end of this period longer until 2018-03-21 23:59:00 
# # This is needed in order to take in consideration pH from March 2018 with a calibration E0 lower (-1.4) than the next period (-0.38).
# sfinterv[5] <- ymd_hms("2018-03-22 23:59:59")
# #  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
# # sfinterv[6] <- ymd_hms("2018-04-24 18:00:00")
# #  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
# # sfinterv[14] <- ymd_hms("2019-01-29 16:00:00")
# 
# #sfinterv <-sort(unlist(sfinterv, use.names=FALSE))
# # set deployment period between 2 spectro measurements.

@@

# pco2_contros_xts <-
#   dplyr::select(d_all, datetime, voltINT, voltEXT, sal_fb, temp_insitu_ctd, ph_s_sf_temp_insi)
# pco2_contros_xts <-
#   as.xts(pco2_contros_xts, order.by = d_all$datetime)
# dygraph(pco2_contros_xts,
#         group = "awipev",
#         main = "<i>p</i>CO<sub>2</sub>",
#         ylab = "<i>p</i>CO<sub>2</sub>") %>%
#   dySeries(
#     axis = "y2",
#     "voltINT",
#     label = "voltINT",
#     color =  RColorBrewer::brewer.pal(5, "Dark2")[1],
#     strokeWidth = 0,
#     pointSize = 2
#   ) %>%
#   dySeries(axis="y2",
#     "voltEXT",
#     label = "voltEXT",
#     color =  RColorBrewer::brewer.pal(5, "Dark2")[2],
#     strokeWidth = 0,
#     pointSize = 2
#   ) %>%
#    dySeries(
#     "temp_insitu_ctd",
#     label = "temp_insitu_ctd",
#     color =  RColorBrewer::brewer.pal(5, "Dark2")[3],
#     strokeWidth = 0,
#     pointSize = 2
#   ) %>%
#    dySeries(
#     "sal_fb",
#     label = "sal_fb",
#     color =  RColorBrewer::brewer.pal(5, "Dark2")[4],
#     strokeWidth = 0,
#     pointSize = 2
#   ) %>%
#    dySeries(
#     "ph_s_sf_temp_insi",
#     label = "ph_s_sf_temp_insi",
#     color =  RColorBrewer::brewer.pal(5, "Dark2")[5],
#     strokeWidth = 0,
#     pointSize = 4
#   ) %>%
#   dyHighlight(
#     highlightCircleSize = 8,
#     highlightSeriesBackgroundAlpha = 0.5,
#     hideOnMouseOut = TRUE
#   ) %>%
#   dyLegend(show = "follow")   %>%
#   dyAxis("y2",valueRange = c(-2,2))%>%
#   dyOptions(
#     drawGrid = TRUE,
#     drawPoints = TRUE,
#     pointSize = c(1, 8, 1),
#     useDataTimezone = TRUE
#   ) %>%
#   dyRangeSelector(height = 30, dateWindow = NULL)

@@

####
## calculation of E0INT25/E0EXT25 ##
##     new sf_calib function      ##
####
calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_insi, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
# put number of deployment 
calib_spectro$deployment_sf <- d_all$deployment_sf

@@

# add spectro points that cannot be taken into consideration (some ancillary data T and/or S not available)
# shown as white triangles on the plot
d_all <- d_all %>%
  dplyr::mutate(
    pH_s_sf_no_calb = ifelse(
      datetime == as.POSIXct("2018-04-16 07:00:00") |
        datetime == as.POSIXct("2018-12-14 10:00:00") |
        datetime == as.POSIXct("2019-01-18 11:00:00"),
      ph_s_sf_temp_insi,
      NA
    )
  )

@@

seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf, pH_s_sf_no_calb)
seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
dygraph(seafet_depth_xts, group = "depth", main="pH seaFET (ref + corrected + raw)", ylab="pHT") %>%
dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 3) %>%
dySeries("ph_s_sf_temp_insi", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
dySeries("pH_s_sf_no_calb", label = "pH spectro no calibration", color =  "black", pointShape = "triangle", strokeWidth = 0, pointSize = 6 ) %>%
dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="UTC"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="UTC"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="UTC"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="UTC"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= Sys.Date(), color = "#E0E0E0") %>%
  dyLegend(show = "auto")   %>%
  dyAxis("y2",valueRange = c(-2, 2)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)

@@

```{r pHs comparaison sf spectro, echo=FALSE, message= FALSE, warning=FALSE}
# Spectro / seafet
# fit <- lmodel2(data = d_all,  ph_s_sf_temp_insi ~ pHint_tot_sf , nperm = 99)
#
# p_sf_spectro <-  ggplot(d_all,aes(x=pHint_tot_sf, y= ph_s_sf_temp_insi, label = month))+
#   geom_text( aes(color=factor(month))) +
#   scale_color_discrete(guide = "none")+
#  geom_abline(slope=1, intercept =0, linetype = "dashed") +
#   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
#   labs(title = paste("pH spectro vs pH seaFET","\n Adj R2 = ", signif(fit$rsquare, 3),
#                      "; Intercept =", signif(fit$regression.results[2,2], 3),
#                      "; Slope =", signif( fit$regression.results[2,3], 3),
#                      "; P =", signif(fit$P.param, 3))) +
#   theme(aspect.ratio=1,plot.title = element_text(size=7)) +
#     coord_fixed(ratio = 1 , xlim=c(8,8.2), ylim=c(8,8.2))+
#   labs(x="pH seaFET", y="pH spectro, 4°C ", color = "Months") + theme_bw()
# p_sf_spectro
```

@@

#### Script awipev-co2.Rmd which runs locally
* reads locally fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds
* sal_mix: when ferrybox data (sal_fb) are missing, they are replaced by data from the profiling ctd for depths > 8 m (sal_insitu_ctd_9m)
* temp_mix: when data of in situ temperature at 11 m (temp_insitu_11m) are missing, they are replaced by data from the profiling ctd for depths > 8 m
* pco2_calc: pco2 calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
* calibrate seafet pH
    - ph_s_sf_temp_insi: pH spectro seaFET pH insi calculé avec AT interpolée + temp_mix +sal_mix
    - E0int25_sf: calculé à partir du voltage interne + ph_s_sf_temp_insi (temp 11m + temp_insitu_ctd_9m si trous) + temp CTD 9m + sal CTD 9m (calib seaFET fonction 1)
    - phint_tot_sf: calculé à partir du voltage interne + E0 + temp CTD + sal CTD (calib seaFET fonction 2)
* ph_calc: pH calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
* despike pH seaFET
* calibrate durafet pH
    - ph_s_dur_temp_fb: pH spectro durafet pH insi calculé avec AT interpolée + temp_fb +sal_fb
* Relation at / sal_mix 
* at_calc: calculé from sal_mix
* saves locally d_all.rds which comprises all variables plus those generated in the script
